Cosmological Evidences of Dark Matter through the CMB

### 2018-12-24 paper/main.tex
new section started

\title{Cosmological Evidences of Dark Matter through the CMB}
\author{Lorenzo Speri}
\date{}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
% ---- Maths -------
\usepackage{amsmath}
\usepackage{amsthm}
% ---- Links -------
\usepackage{hyperref}

@@

\subsection{to be put in the paper or at the end}
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-structure of the paper \\

@@

\begin{figure}
\centering
    \textbf{CMB spectrum}\par\medskip
\centering
   {\includegraphics[height=8cm]{blackbody.png}}
\caption{}
\label{cobe_blackbody}
\end{figure}

@@

\section{Content of the Universe}
The General Theory of Relativity is the best theory of gravity that we have, so far. So,  
\begin{itemize}
\item Assumptions: working with the $\Lambda$CDM model
\item General relativty
\item Friedmann equations
\end{itemize}

>>>>

\title{Cosmological Evidences of Dark Matter through the CMB}
\author{Lorenzo Speri}
\date{}
%\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
% ---- Maths -------
\usepackage{amsmath}
\usepackage{amsthm}
% ---- Links -------
%\usepackage{hyperref}
% citation color
\usepackage[colorlinks=true,citecolor=blue]{hyperref}

@@

\subsection{to be put in the paper or at the end}
-practical Motivation for studyinbg the cmb: nice spectrum black body spectrum: physics well know, very intense radiation\\
which info can we get from the cmb: Big bang, maater and energy content of the universe---dark matter is a big part of the matter content it influenced the spectrum  of the CMB ---- so it played a role.\\
-\textbf{structure of the paper} \\

@@

\begin{figure}
\centering
    \textbf{Cosmic Microwave Background  Spectrum}\par\medskip
\centering
   {\includegraphics[height=8cm]{blackbody}}
\caption{}
\label{cobe_blackbody}
\end{figure}

@@

\section{Content of the Universe}
The experimental results from the observations of the Cosmic Microwave Background provide important details about energy-matter content of the Universe. 
We now need to set the theoretical framework we want to use to analyze the observations of the CMB.\\
We assume that the observable properties of the Universe are isotropic and there is not a preferred direction. Therefore, the Universe is assumed to be homogenous and isotropic at enough large scales $> 100$ Mpc, at least up to the observable universe.\\
Another important assumption is that there exists a class of observers at rest with respect to the Cosmic Microwave Background \citep{bartelmannStandardModelCosmology}. These observers do not see the dipole pattern typical of a moving observer with respect with the CMB. 
For instance the Earth is not at rest with respect to the CMB as we can notice from the second panel in Figure (\ref{cobe_map}).\\

The best theory of gravity that can tell us accurately how the different components of the Universe evolved is the General Theory of Relativity, so far.
Therefore, we assume the correctnes of the General Theory of Relativity.

 the energy-matter contentandis carried out using different 
The General Theory of Relativity is the best theory of gravity that we have, so far. So,  
\begin{itemize}
\item Assumptions: working with the $\Lambda$CDM model
\item General relativty
\item Friedmann equations
\end{itemize}
